A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\medskip
The discretised saturation and Darcy equations are solved using a multigrid-like approach as described by \citeauthor{pavlidis2016}~\cite{pavlidis2016}. The numerical formulation is fully described by \citeauthor{Gomes_2017}~\cite{Gomes_2017} (see also \cite{adam_2016, salinas2015}). These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{Gomes_2017, jackson_2013,salinas_2018}). Although, the numerical formulation used here is relatively new, it is not the focus of this work. The result and discussion section (Section \ref{section:results_discussion}) refers to \citet{dawe_2008} for validation of the numerical formulation with respect to the 2D simulation. However, more extensive validation tests can be found in the aforementioned references \cite{adam_2016, Gomes_2017,jackson_2013, pavlidis2016, salinas2015}.

>>>>

\medskip
The discretised saturation and Darcy equations are solved using a multigrid-like approach as described by \citeauthor{pavlidis2016}~\cite{pavlidis2016}. The numerical formulation is fully described by \citeauthor{Gomes_2017}~\cite{Gomes_2017} (see also \cite{adam_2016, salinas2015}). These numerical methods are embedded in the next-generation flow simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} (a full description of the model can be found in \cite{Gomes_2017, jackson_2013,salinas_2018}). Although, the numerical formulation used here is relatively new, it is not the focus of this work. The result and discussion section (Section \ref{section:results_discussion}) refers to \citet{dawe_2008} for validation of the numerical formulation with respect to the 2D simulation. However, extensive model and software quality assurance (\ie verification and validation tests) can be found in the aforementioned references \cite{adam_2016, Gomes_2017,jackson_2013, pavlidis2016, salinas2015}.
